jstor: Parsing XML - Lessons From Writing a Package

### 2018-10-01 draft.Rmd
need to use images instead of widgets for .md
simplify code slightly

The difference is not huge (~50sec for 500000 documents), but my actual layout
was a lot more complex, since it was using nested structures in a weird way:

```{r}
# dummy function for getting the data
get_authors <- function() {
  tibble::tribble(
    ~first_name, ~last_name, ~author_number,
    "Pierre",    "Bourdieu", 1,
    "Max",       "Weber",    2,
    "Karl",      "Marx",     3
  )
}

# this approach made sense to me, since the data structure was indeed nested,
# and it seemed similar to the approach of mutate + map + unnest.
old_approach <- function() {
  res <- tibble::data_frame(id = "1",
                            authors = list(get_authors()))

@@

# this is obviously a lot simpler
new_approach <- function() {
  data.frame(id = "1",
             authors = get_authors())
}

microbenchmark::microbenchmark(
  old = old_approach(),
  new = new_approach()
)

@@

Unfortunately, using profvis for
such small and fast functions does not work well out of the box:

@@

```{r}
profvis::profvis({

@@

  authors <- get_authors()
  purrr::rerun(500, old_approach(authors))
})
```

@@

  authors <- get_authors()
  purrr::rerun(500, new_approach(authors))})
```

>>>>

The difference is not huge (~50sec for 500,000 documents), but my actual layout
was a lot more complex, since it was using nested structures in a weird way:

```{r}
# dummy function for getting the data
authors <- tibble::tribble(
  ~first_name, ~last_name, ~author_number,
  "Pierre",    "Bourdieu", 1,
  "Max",       "Weber",    2,
  "Karl",      "Marx",     3
)

# this approach made sense to me, since the data structure was indeed nested,
# and it seemed similar to the approach of mutate + map + unnest.
old_approach <- function(authors) {
  res <- tibble::data_frame(id = "1",
                            authors = list(authors))

@@

# this is obviously a lot simpler
new_approach <- function(authors) {
  data.frame(id = "1",
             authors = authors)
}

microbenchmark::microbenchmark(
  old = old_approach(authors),
  new = new_approach(authors)
)

@@

Unfortunately, using `profvis` for
such small and fast functions does not work well out of the box:

@@

```{r, eval=FALSE}
profvis::profvis({

@@

  purrr::rerun(500, old_approach(authors))
})
```

![](screenshots/old_version.png)

@@

  purrr::rerun(500, new_approach(authors))})
```

![](screenshots/new_version.png)
